Waving and swaying

### 2014-08-15 Paper/grass.tex

respectively, momentum and mass balance equation expanded in first order of perturbed variable yields.
\small

@@

\frac{\del u}{\del t}+U\frac{\del u}{\del x}+v\frac{\del U}{\del y} &= -\frac{1}{\rho}\frac{\del p}{\del x}+\frac{\mu}{\rho}\nabla^2u-2S(y) C_{N}dN_{g}Uu\\
\frac{\del v}{\del  t}+ U\frac{\del v}{\del x} &= -\frac{1}{\rho}\frac{\del p}{\del y}+\frac{\mu}{\rho}\nabla^2v, \hspace{0.3cm} \nabla\cdot\bu=0\\

@@

\normalsize
Momentum and mass balance equation can be non-dimensionlize using half channel height $H$, associated advection time H/$U_0$ and velocity $U_0$.
With these scaling along with the use of stream function $\psi$ with $u = \psi_{y}, v= -\psi_x$ to satisfy mass balance; momentum and mass balance can be combined 
into a single equation.
\small
R \left[ (\del_t+\del_x U )\grad^2\psi - U_{yy}\psi_x \right] = \grad^4\psi-\frac{\del}{\del_y}\left({2}\frac{H^3}{\delta^3}S(y) U\psi_y\right)
\normalsize
%In most of recent work on honami/monami base profile have been approximated to a plane mixing layer profile having inflection point near top of canopy, It is also argued that 
%It is instability associated with inflection of mean velocity which is responsible for coherent eddies traveling on top of canopies. In our calculation we get base velocity
%profile by hydrodynamic balance between pressure, drag and diffusive force which also results in a velocity profile with inflection point near top of canopy with additional property 
%of having been produced through equation of motion itself.\newline
%We performed stability analysis on two different kind of base flow namely (1) flow driven by constant pressure gradient between two parallel plate (2) constant pressure gradient driven 
%flow with zero shear at top. We use following scaling to non-dimensionlize equation of motion
%Using half channel height $H$ of and associated advection time H/$U_{0}$, we use following scaling to non-dimensinlize equation 
%of motion
%   \[ u = U_{0}\bar{u},\hspace{1cm} y = (H/2)\bar{y}, \hspace{1cm} \text{with}\hspace{2mm} U_{0}=\frac{(dP/dx)H^2}{4\mu} \]
where $R= {\rho U_0 H}/{\mu}$ is Reynolds number. Seeking wave solution in form of $\left(u,v,\psi \right)= \left(\hat u, \hat v, \hat\phi \right)e^{ikx+\sigma t}$, 
we get modified Orr-Sommerfield equation. The eigenvalue $\sigma$ for a given $k$ provides growth rate and frequency associated with a perturbation of wavelength $2\pi/k$.
\small

@@

\normalsize

@@

Solution of generalized Orr-Somerfield equation predicts a critical Reynolds number as function of grass number density, below which the flow is stable 
(Figure\ref{Re_vs_delta}). The solution also predicts a critical wavenumber $k$ with maximum growth rate.
The variation of critical wave number with the variation in $\delta$ for different grass height is shown in Figure \ref{K_vs_shear}, where we can observe that above a 

@@

%    This variation of critical 
%wavenumber with shear layer thickness can be divided into three distinct region. First, the region where critical wavelength does not increases linearly with the
%increase of the shear layer thickness, this region occur for canopies with thick shear layer $H/\delta <10$. Second region identified as shear layer region, where variation in critical
%wavelength is proportional to the variation in shear layer thickness, the instability in this region can be understood to arise from a mechanism similar to Kelin-Helmholtz instability 
%observed in the free shear flow. Third, the region where critical wavelength does not vary with the variation of shear layer thickness. The boundary of these region depends on 
%submergence ratio and the shear layer thickness experienced by the canopy.

>>>>

respectively, momentum and mass balance equation expanded in first order of perturbed variable yields

@@

\frac{\del u}{\del t}+U\frac{\del u}{\del x}+v\frac{\del U}{\del y} &= -\frac{1}{\rho}\frac{\del p}{\del x}+\frac{\mu}{\rho}\nabla^2u-2S(y) C_{N}dN_{g}Uu, \\
\frac{\del v}{\del  t}+ U\frac{\del v}{\del x} &= -\frac{1}{\rho}\frac{\del p}{\del y}+\frac{\mu}{\rho}\nabla^2v, \hspace{0.3cm} \nabla\cdot\bu=0.

@@

Momentum and mass balance equation can be non-dimensionlize using half channel height $H$, associated advection time H/$U_0$ and velocity $U_0$. We are left with three non-dimensional parameters in the model, viz. the Reynolds number $R= {\rho U_0 H}/{\mu}$, the drag parameter $\delta/H$, and the submergence ratio of the grass $h_g/H$. With these scaling along with the use of stream function $\psi$ with $u = \psi_{y}, v= -\psi_x$ to satisfy mass balance; 
% momentum and mass balance can be combined  into a single equation.
% \begin{equation}
% R \left[ (\del_t+\del_x U )\grad^2\psi - U_{yy}\psi_x \right] = \grad^4\psi-\frac{\del}{\del_y}\left({2}\frac{H^3}{\delta^3}S(y) U\psi_y\right).
% \end{equation}
Seeking wave solution in form of $\left(u,v,\psi \right)= \left(\hat u, \hat v, \hat\phi \right)e^{ikx+\sigma t}$,  we get modified Orr-Sommerfield equation. The eigenvalue $\sigma$ for a given $k$ provides growth rate and frequency associated with a perturbation of wavelength $2\pi/k$.
% \small

@@

% \normalsize

@@

Solution of \eqref{Orr-somerfield} predicts a critical $R$ as function of grass number density, below which the flow is stable (Re($\sigma$)$<0$) and above which it is unstable (Re($\sigma$)$>0$),
as shown in Figure\ref{Re_vs_delta}. The solution also predicts a finite critical wavenumber $k$ corresponding to this threshold for instability shown in Figure \ref{K_vs_shear}. 
\shreyas{Needs language clean up from here on. Describe the most important observation. The details are to be explained in the longer paper.}
we can observe that above a 

@@
